Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-11-02 robdml.tex
tex

@@

According to the results, EST[$\mathcal{R}$] achieves a relatively high R@1
when $\eta{=}8$, but suffers from a drastic drop in R@1 when $\eta$ is
increased to $32$.
%
Nevertheless, EST[$\mathcal{R}$] only lead to a moderate robustness in all
settings compared to other methods.
%
Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result
in even lower ERS based on the observations in previous subsections, and
EST has been greatly outperformed by ACT~\cite{robrank}.

>>>>

\oo{regular and max can be expressed as two boundary cases of HM}

@@

According to the results, EST[$\mathcal{R}$] achieves a relatively high R@1
when $\eta{=}8$, but suffers from a drastic drop in R@1 when $\eta$ is
increased to $32$.
%
Nevertheless, EST[$\mathcal{R}$] only lead to a moderate robustness in all
settings compared to other methods.
%
Experiments for EST[$\mathcal{S}$] is omitted as it is expected to result
in even much lower ERS based on the observations in previous subsections, and
EST has been greatly outperformed by ACT~\cite{robrank}.
